Stochastic blockmodeling of relational event dynamics

### 2012-06-01 docs/discussion.tex
Work on prediction

%This analysis suggests 
Our approach has the ability to uncover systematic differences in dynamic behaviors among subsets of nodes.
% across a variety of data sets.
In Section \ref{sec:experiments} we show the model has improved predictive accuracy over baseline methods on real data with respect to ranking tasks and the likelihood of unobserved data.
In particular, we show that our proposed approach leads to improved predictive accuracy when compared to both (a) relational event models that lack latent clusters, and (b) stochastic blockmodels for count data, both of which are both special cases of our model.
Though prediction is not the main focus of the model, the results provide some evidence that having latent structure (i.e. K>1) can lead to improvements in predictive power. Our prediction results show that it is easy to overfit with this model. If we restrict to K=2 on these small data sets, we systematically outperform the K=1 model. {\red(TODO: confirm this)}
  However, as K increases beyond 2 (e.g., for the unrestrained CRP prior), the model is prone to overfit. This is not surprising, given that the number of fitted parameters scales as the square of the number of components K in the model. A natural future direction worth exploring for this model is a class of priors that are more resistant to overfitting.

>>>>

%This analysis suggests 
Our approach has the ability to uncover systematic differences in dynamic behaviors among subsets of nodes.
% across a variety of data sets.
In Section \ref{sec:experiments} we show the model has improved predictive accuracy over baseline methods on real data with respect to ranking tasks and the likelihood of unobserved data.
In particular, we show that our proposed approach leads to improved predictive accuracy when compared to both (a) relational event models that lack latent clusters, and (b) stochastic blockmodels for count data, both of which are both special cases of our model.
Though prediction is not the main focus of the model, the results provide some evidence that having latent structure (i.e. K>1) can lead to improvements in predictive power. Our prediction results show that it is easy to overfit with this model. 
%If we restrict to K=2 on these small data sets, we systematically outperform the K=1 model. 
%{\red (TODO: confirm this)}
 As K increases beyond 2 (e.g., for the unrestrained CRP prior), the model is prone to overfit. This is not surprising, given that the number of fitted parameters scales as the square of the number of components K in the model. A natural future direction worth exploring for this model is a class of priors that are more resistant to overfitting.
